% LaTeX file for resume 
% This file uses the resume document class (res.cls)
\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}
\usepackage[left=0.5in, right=1in, top=0.6in]{geometry}
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document} 

\begin{center}
{\Large\bf Joel S. Williamson}
{\center \href{mailto:joel@joelwilliamson.ca}{joel@joelwilliamson.ca}\\\url{www.joelwilliamson.ca}\\\url{www.github.com/joelwilliamson}\\
(519) 591-5635\\21 King St. N, Waterloo ON, N2J 2W6 }
\end{center}
\vspace{-1cm}                 
\begin{resume}

\section{PROGRAMMING SKILLS}          
  \vspace{3mm}
    Extensive development experience in C++\\
    Proficient with OCaml, C, Python, LabVIEW\\
    Familiar with Haskell, JavaScript, Assembly (MIPS and x86\_64), Verilog 
 

 
\section{EXPERIENCE}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Telefund Associate} \>Rensselaer Fund     \>Fall 1987-Present\\
                             \>Troy, NY
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Generated alumni and parent support to reduce tuition,          
    increase scholarship and financial aid funds; averaging 80          
    percent pledge rate. Top three percent associate.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Team Programmer} \>Group W Cable, Westinghouse Corp \> ~~~~~~ Summer 1987\\
                          \>Mahway, NJ
   \end{tabbing}\vspace{-20pt}
    Liaison between accounting department and controller,          
    provided assistance with invoice liabilities after          
    divestiture of Group W Cable by Westinghouse.
   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Sales Assistant}  \>AP Technical Sales Inc. \> Summers  1985-86\\
                          \>Palisades Park, NJ
   \end{tabbing}\vspace{-20pt}
    Duties included telemarketing, data entry, and invoicing.          
    Successfully converted catalog inquiries to sales          
    opportunities by telemarketing program.          


\section{COMPUTER SKILLS}          
    Extensive knowledge of hardware and software for IBM PC and          
    MTS. \\         
    Proficient programming skills in COBOL, WATFIV (FORTRAN), and          
    BASIC.          
 
\section{WORK EXPERIENCE}
  \vspace{3mm}
    {\bf Research Developer} -- Professor Richard Mann, University of Waterloo	\hfill Winter 2014\\
    \vspace{-2mm}
   \begin{itemize}
    \item Developed hardware control software in LabVIEW for recording and modelling noise pollution
    \item Collaborated with the kernel developer creating low level drivers for microphone
    \item Improved user experience for data collection through interface design
    \item Researched the effect of subsonic noise on human physiology
    
   \end{itemize}

   
\section{EDUCATION}          
  \vspace{3mm}
    University of Waterloo\hfill September 2009 -- Present\\
    Candidate for Bachelor of Science\hfill Expected Completion 2015\\
    Honours Computational Science, Specialization in Physics
    \vspace{-3mm}
    
    {\bf Scholarships} -- Undergraduate Research Assistantship, President's Scholarship
    \vspace{-3mm}
    
    {\bf Relevant Courses}
      \vspace{1mm}
      \begin{itemize}
       \item Computer Architecture, Operating Systems, Networks and Distributed Systems, Logic and Computation, Software Development, Algorithms and Data Structures
      \end{itemize}
    
    
\section{COMMUNITY INVOLVEMENT}
    \vspace{3mm}
    {\bf Rangemaster} -- Archery Club, University of Waterloo\hfill 2012 -- present\\
    \vspace{-2mm}
   \begin{itemize}
    \item Regularly trained new members in archery essentials and safety procedures
    \item Designed curriculum to improve beginner progression
    \item Maintained and repaired specialized club equipment
   \end{itemize}
   
%   {\bf Member} -- Computer Science Club, University of Waterloo \hfill 2013 -- present\\
%   \vspace{-2mm}
%   \begin{itemize}
%    \item Attended biweekly screening of C++ GoingNative lectures for three months among others
%   \end{itemize}

\section{INTERESTS}
  \vspace{3mm}
  Skiing (CSIA Certified Instructor), Archery, Reading, Biking, Gymnastic Rings, Cooking
  
 
\end{resume}
\end{document}
